Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2018-11-01 Manuscript/manuscript.tex
Update methods text

The polarization of electrons in ECC-lipids uses the implicit method termed electronic continuum correction (ECC). \cite{leontyev09, Pluharova2014, martinek17, melcr18} 
In this method, a system of polarizable particles is represented with an equivalent system of particles with fixed charges. 
This is practically achieved rescaling the charges with a pre-determined scaling factor, $f_q$,
which is derived from the high-frequency dielectric constant of electrons, $\epsilon_{el}$, as
\begin{equation}
f_q = \frac{1}{\sqrt{\epsilon_{el}}} .
\end{equation}
The value of $\epsilon_{el}$ for water solutions is $\epsilon_{el} = 1.78$ \cite{leontyev09},
hence, the scaling factor for aquaeous environments yields $f_q \approx 0.75$.

It is important to note that the value of the high frequency dielectric constant  
is around 2 for almost any biologically relevant environment \citep{leontyev11}. 
This means that even interfaces like biological membranes do not contain discontinuities of the electronic continuum. 
The dielectric discontinuity in a lipid bilayer thus arises only 
from the orientational polarization of the molecules, which is accounted for explicitly in standard MD simulations.  
Therefore, the same correction for the electronic polarizability can be  
applied throughout the lipid bilayer/aqueous solution interface.

In the case of POPS, which is a monovalently negatively charged lipid, 
we used exactly the pre-determined scaling factor 
to represent the effects of electronic polarization
yielding a total charge of $-0.75$ in the ECC formalism. \cite{martinek17, leontyev09, melcr18}
Similarly to the ECC-POPC model, we changed the charges only of the polar parts of the phospholipid,
i.e., charges on all atoms except on alkyl tails, 
which do not encounter direct contacts with ions.

Note that we used a different scaling factor $f_q = 0.8$ 
to for the ECC-POPC model. \cite{melcr18}
Compared to POPS, POPC is a zwitterionic neutral molecule with a zero total charge; 
scaling it by any factor does not affect it. 
Partial charges of the atoms in POPC are not physical observables, 
and vary greatly between different models. \cite{botan15, catte16, nmrlipids_proj4, Pluhackova2016}
The choice of a larger scaling factor in ECC-POPC represents the fact that 
the set of partial charges in the initial model for ECC-POPC, the Lipid14 model \cite{dickson14}, 
was determined in the beginning as less polar compared to other models.

>>>>

The lack of electronic polarizability has been a concern since the
early days of classical MD simulations of lipids \cite{jonsson86,egberts94, berendsen1996},
where the atomic charges were scaled by a factor of 1/2 to effectively
include the electrostatic screening from the missing electronic polarizability.
The electronic continuum correction (ECC) is a more sophisticated version of the charge scaling.
In ECC, the charges are rescaled with a pre-determined scaling factor, $f_q$,
\begin{equation}
  f_q = \frac{1}{\sqrt{\epsilon_{el}}} ,
\end{equation}
where $\epsilon_{el}$ is the high-frequency dielectric constant of electrons.
The value of $\epsilon_{el} = 1.78$ for water solutions gives the scaling
factor of $f_q \approx 0.75$ for aquaeous environments \cite{leontyev09}.
This has been recently applied to improve classical models for ions and
other biomolecules \cite{Pluharova2014, martinek17, melcr18}
\todo{Pavel can probably update this}.

Recently we applied the ECC also to the Amber based lipid14 force field \cite{dickson14} to
improve the cation binding affinity to zwitterionic POPC lipid bilayers \cite{melcr18}.
In contrast to the total charge of ions, the partial charges in force fields of zwitterionic
depend on the methods used to derive the force field which may already partially include the
electronic polarizability effects. Therefore, the optimal scaling factor for charges in
zwitterionic lipids may be larger than the theoretically derived $f_q \approx 0.75$.
In the recent work, we found optimal results for cation binding affinity and
bilayer structural properties when the partial charges and Lennard-Jones $\sigma$
parameters of headgroup, glycerol backbone, and carbonyl regions of the lipid14 POPC model
were scaled with the factors of $f_q = 0.8$ and $f_\sigma = 0.89$, respectively \cite{melcr18}.

%Compared to POPS, POPC is a zwitterionic neutral molecule with a zero total charge; 
%scaling it by any factor does not affect it. 
%Partial charges of the atoms in POPC are not physical observables, 
%and vary greatly between different models. \cite{botan15, catte16, nmrlipids_proj4, Pluhackova2016}
%The choice of a larger scaling factor in ECC-POPC represents the fact that 
%the set of partial charges in the initial model for ECC-POPC, the Lipid14 model \cite{dickson14}, 
%was determined in the beginning as less polar compared to other models.

Here, we apply the ECC to the Amber based lipid17 parameters \cite{could18} of POPS lipid with
a total monovalent negative charge. In this case we apply the scaling factor of $f_q = 0.75$ 
also to the lipid because it carries a physical total charge similar to the ions in solution and
the lipid charges has to neutralize the counterion charges in simulations.
For the Lennard-Jones $\sigma$ parameters, we used the same scaling factor of $f_\sigma = 0.89$
as in the ECC-POPC model \cite{melcr18}.
%we used exactly the pre-determined scaling factor 
%to represent the effects of electronic polarization
%yielding a total charge of $-0.75$ in the ECC formalism. \cite{martinek17, leontyev09, melcr18}
Similarly to the ECC-POPC model \cite{melcr18}, we applied the ECC only to the
headgroup, glycerol backbone, and carbonyl regions.
%polar parts of the phospholipid,
%i.e., charges on all atoms except on alkyl tails, 
%which do not encounter direct contacts with ions.

%It is important to note that the value of the high frequency dielectric constant  
%is around 2 for almost any biologically relevant environment \citep{leontyev11}. 
%This means that even interfaces like biological membranes do not contain discontinuities of the electronic continuum. 
%The dielectric discontinuity in a lipid bilayer thus arises only 
%from the orientational polarization of the molecules, which is accounted for explicitly in standard MD simulations.  
%Therefore, the same correction for the electronic polarizability can be  
%applied throughout the lipid bilayer/aqueous solution interface.
